Yeast RNA-seq 48 sample simulation study

### 2018-02-14 datasets/RNA-Seq/yeast48-replicates-benchmarkFDR.Rmd
Add log2FC to truth; don't re-run if results file present

  sb <- bd %>% buildBench(data=geneExp, parallel = F, truthCols = "qvalue")

@@

null5 <- mclapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd,
                   mc.cores=cores)
```

@@

# metrics = ""TPR"   "FPR"   "TNR"   "FNR"   "rejections"  "FWER"   "rejectprop"
plotsim_average(res5, met="rejections",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) 
plotsim_average(res5, met="TNR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE)

@@

null10 <- mclapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd,
                   mc.cores=cores)
```

@@

# metrics = ""TPR"   "FPR"   "TNR"   "FNR"   "rejections"  "FWER"   "rejectprop"
plotsim_average(res10, met="rejections",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) 
plotsim_average(res10, met="TNR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE)

@@

de5 <- mclapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd,
                   mc.cores=cores)
```

@@

```{r}
res5d <- plotsim_standardize(de5, alpha = seq(0.01, 0.20, 0.01))

# metrics = ""TPR"   "FPR"   "TNR"   "FNR"   "rejections"  "FWER"   "rejectprop"
plotsim_average(res5d, met="rejections",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) 
plotsim_average(res5d, met="FPR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) 
plotsim_average(res5d, met="TPR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE)

if (numberMethodsReject(res5d, alphacutoff=ualpha, filterSet=excludeSet) >= 3){
  aggupset(de5, alpha=ualpha, supplementary = FALSE, return_list = FALSE) 
}else{
  message("Not enough methods found rejections at alpha ", ualpha, 
          "; skipping upset plot")
}

@@

de10 <- mclapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd,
                   mc.cores=cores)
```

@@

# Save results objects

```{r}
system("mkdir -p yeast48-results")
saveRDS(null5, file="yeast48-results/null5.rds")
saveRDS(null10, file="yeast48-results/null10.rds")
saveRDS(de5, file="yeast48-results/de5.rds")
saveRDS(de10, file="yeast48-results/de10.rds")
```

>>>>

  sb <- bd %>% buildBench(data=geneExp, parallel = F, 
                          truthCols = "qvalue")
  rowData(sb)$log2FC <- geneExp$effect_size

@@

system("mkdir -p yeast48-results")

if (!file.exists("yeast48-results/null5.rds")){
  null5 <- mclapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd,
                   mc.cores=cores)
  saveRDS(null5, file="yeast48-results/null5.rds")
}else{
  null5 <- readRDS(file="yeast48-results/null5.rds")
}

@@

plotsim_average(res5, met="rejections",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) 
plotsim_average(res5, met="TNR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE)

@@

if (!file.exists("yeast48-results/null10.rds")){
  null10 <- mclapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd,
                   mc.cores=cores)
  saveRDS(null10, file="yeast48-results/null10.rds")
}else{
  null10 <- readRDS(file="yeast48-results/null10.rds")
}

@@

plotsim_average(res10, met="rejections",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) 
plotsim_average(res10, met="TNR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE)

@@

if (!file.exists("yeast48-results/de5.rds")){
  de5 <- mclapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd,
                   mc.cores=cores)
  saveRDS(de5, file="yeast48-results/de5.rds")
}else{
  de5 <- readRDS(file="yeast48-results/de5.rds")
}
```

@@

```{r}
  mat <- ( assays( de5[[1]] )[["qvalue"]] < 0.1 )
  dfCov <- data.frame(
    covariate = sizesAll,
    methods=factor( rep( names( allLenghts ), sapply( allLenghts, length ) ), 
                    levels=names(allLenghts)  ) )
  pl <- ggplot( dfCov, aes( methods, trans(covariate), col=methods) ) +
    geom_boxplot( ) + theme(legend.position="top", 
                            axis.text.x=element_blank(), 
                            legend.direction="vertical") +
    labs(col="", y="Covariate", x="") + guides(color=guide_legend(ncol=2))
  pl
}

res5d <- plotsim_standardize(de5, alpha = seq(0.01, 0.20, 0.01))

plotsim_average(res5d, met="rejections",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) 
plotsim_average(res5d, met="FPR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE) 
plotsim_average(res5d, met="TPR",filter_set = excludeSet,
                merge_ihw = TRUE, errorBars=TRUE)

if (numberMethodsReject(res5d, alphacutoff=ualpha, filterSet=excludeSet) >= 3){
  aggupset(de5, alpha=ualpha, supplementary = FALSE, return_list = FALSE)

}else{
  message("Not enough methods found rejections at alpha ", ualpha, 
          "; skipping upset plot")
}

@@

if(!file.exists("yeast48-results/de10.rds")){
  de10 <- mclapply(X=1:B, FUN=simulateOneSplit, rseed=rseed, dds=dds, 
                   resFULL=resFULL, nDE=nDE, sampleSize=sampleSize, bd=bd,
                   mc.cores=cores)
  saveRDS(de10, file="yeast48-results/de10.rds")
}else{
  de10 <- readRDS(file="yeast48-results/de10.rds")
}
```

@@
